---
title: "HW4"
author: "Ilia Sheshukov"
date: "April 13, 2019"
output:
  html_document: default
  pdf_document: default
---

Выполнить задания: 10M3-10M5 соответственно (3 варианта)
Выполнить задания (рассказать суть задачи, рассказать подход, показать результаты):  10H1, 10H3 (a)-(b), 10H4 (a)-(b) (игнорировать пункты про WAIC) соответственно соответственно (3 варианта)

# 10M5
What would it imply to use a logit link for the mean of a Poisson generalized linear model? -- То, что среднее будет лежать между 0 и 1.

# 10H4
The data contained in data(salamanders) are counts of salamanders (Plethodon elongatus)
from 47 different 49-m 2 plots in northern California. 166 The column SALAMAN is the count in each
plot, and the columns PCTCOVER and FORESTAGE are percent of ground cover and age of trees in the
plot, respectively. You will model SALAMAN as a Poisson variable.

```{r}
library(rethinking)
data("salamanders")
```
## a
Model the relationship between density and percent cover, using a log-link.

```{r}
f <- alist(
  SALAMAN ~ dpois(lambda),
  log(lambda) <- alpha + beta*PCTCOVER,
  alpha ~ dnorm(0, 1),
  beta ~ dnorm(0, 1)
)

map_ <- map(f, data = salamanders)
stan_ <- map2stan(f, data = salamanders, warmup = 1e4, iter = 1e4)
```
```{r}
X <- seq(from=0,to=100,length.out=30)
Y <- sim(stan_, data = list(PCTCOVER = X))
Y_mean <- apply(X = counts, MARGIN = 2, FUN = mean)
Y_PI <- apply(X = counts, MARGIN = 2, FUN = PI)

plot(SALAMAN ~ PCTCOVER, data = salamanders)
lines(X, Y_mean)
shade(Y_PI, X)
```
## b
Can you improve the model by using the other predictor, FORESTAGE?
```{r}
f <- alist(
  SALAMAN ~ dpois(lambda),
  log(lambda) <- alpha + beta*FORESTAGE,
  alpha ~ dnorm(0, 1),
  beta ~ dnorm(0, 1)
)

map_ <- map(f, data = salamanders)
stan_ <- map2stan(f, data = salamanders, warmup = 1e4, iter = 1e4, chains = 4)

X <- seq(from=0,to=700,length.out=30)
Y <- sim(stan_, data = list(FORESTAGE = X))
Y_mean <- apply(X = counts, MARGIN = 2, FUN = mean)
Y_PI <- apply(X = counts, MARGIN = 2, FUN = PI)

plot(SALAMAN ~ FORESTAGE, data = salamanders)
lines(X, Y_mean)
shade(Y_PI, X)
```