---
title: "HW1"
output: html_notebook
---

```{r}
library(rethinking)
data(homeworkch3)
```

# 2M1(3)

$$ p = \frac{W}{W+L} $$
```{r}
# define grid
p_grid <- seq( from=0 , to=1 , length.out=20 )
# define prior
prior <- rep( 1 , 20 )
# compute likelihood at each value in grid
likelihood <- dbinom( 5 , size=7 , prob=p_grid )
# compute product of likelihood and prior
unstd.posterior <- likelihood * prior
# standardize the posterior, so it sums to 1
posterior <- unstd.posterior / sum(unstd.posterior)
plot( p_grid , posterior , type="b" ,
xlab="probability of water" , ylab="posterior probability" )
```

# 2M2(3)

```{r}
p_grid <- seq( from=0 , to=1 , length.out=20 )
# define prior
prior <- as.integer(p_grid > 0.5)
# compute likelihood at each value in grid
likelihood <- dbinom( 5 , size=7 , prob=p_grid )
# compute product of likelihood and prior
unstd.posterior <- likelihood * prior
# standardize the posterior, so it sums to 1
posterior <- unstd.posterior / sum(unstd.posterior)
plot( p_grid , posterior , type="b" ,
xlab="probability of water" , ylab="posterior probability" )
```

# 3H5

> The model assumes that sex of first and second births are independent. To check this assump-
tion, focus now on second births that followed female first borns. Compare 10,000 simulated counts
of boys to only those second births that followed girls. To do this correctly, you need to count the
number of first borns who were girls and simulate that many births, 10,000 times. Compare the
counts of boys in your simulations to the actual observed count of boys following girls. How does the
model look in this light? Any guesses what is going on in these data?


``` {r}
boys_after_girls <- birth2[birth1 == 0]

# define grid
p_grid <- seq(from = 0, to = 1, length.out = 1000)
# define prior
prior <- rep(x = 1, 1000)
# compute likelihood at each value in grid
likelihood1 <- dbinom(x = sum(boys_after_girls), size = length(boys_after_girls), prob = p_grid)
likelihood2 <- dbinom(x = sum(c(birth1, birth2)), size = length(c(birth1, birth2)), prob = p_grid)
# compute product of likelihood and prior
unstd.posterior1 <- likelihood1 * prior
unstd.posterior2 <- likelihood2 * prior
# standardize the posterior, so it sums to 1
posterior1 <- unstd.posterior1 / sum(unstd.posterior1)
posterior2 <- unstd.posterior2 / sum(unstd.posterior2)
samples1 <- sample(x = p_grid, size = 10000, prob = posterior1, replace = TRUE)
samples2 <- sample(x = p_grid, size = 10000, prob = posterior2, replace = TRUE)
posterior1 <- rbinom(n = 10000, size = length(boys_after_girls), prob = samples1)
posterior2 <- rbinom(n = 10000, size = length(boys_after_girls), prob = samples2)

hist(posterior1, col=rgb(0,0,1,1/4))
hist(posterior2, add=T, col=rgb(1,0,1,1/4))
abline(v = sum(boys_after_girls))
```