---
title: "HW5"
output:
  html_document:
    df_print: paged
---
```
Задание 5 (на 27.04)
Прочитать и осознать Главу 12
Выполнить задания (рассказать суть задачи, рассказать подход, показать результаты): 11E3, 11E4
```

## 11E3. 
`When count data are zero-inflated, using a model that ignores zero-inflation will tend to induce which kind of inferential error?`

Т.к. мы не различаем события приведшие к появлению нуля, то мы не сможем корректно предсказать какой ноль из чего получился.
Получим просто неверное предсказание.

## 11E4. 
`Over-dispersion is common in count data. Give an example of a natural process that might produce over-dispersed counts. 
Can you also give an example of a process that might produce under dispersed counts?`

1. Количество автобусов, приходящих на остановку за час. Можем выяснить среднее и дисперсия будет крутиться где-то недалеко от этого среднего, но на самом деле, автобусы ходят
довольно равномерно в течение дня.
2. Рассматриваем количество людей, которые ходят в бар в день. Подавляющее большинство ходят в пятницу и простая модель это не может учесть.

## 11H6. 
`The data in data(Fish) are records of visits to a national park. See ?Fish for details. The question of interest is how many fish an average visitor takes per hour, when fishing.
The problem is that not everyone tried to fish, so the fish_caught numbers are zero-inflated. As with the monks example in the chapter, there is a process that determines who is
fishing (working) and another process that determines fish per hour (manuscripts per day), conditional on fishing (working). We want to model both. Otherwise we’ll end up with an
underestimate of rate of fish extraction from the park. You will model these data using zero-inflated Poisson GLMs. Predict fish_caught as a function of any of the other variables
you think are relevant. One thing you must do, however, is use a proper Poisson offset/exposure in the Poisson portion of the zero-inflated model. Then use the hours variable to
construct the offset. This will adjust the model for the differing amount of time individuals spent in the park.`

```{r}
library(rethinking)
data(Fish)
d <- Fish
d
```

```{r}
pers_norm <- (d$persons - mean(d$persons))/sd(d$persons)
model <- map(
  alist(
    fish_caught ~ dzipois( p , lambda ),
    logit(p) <- ap + b_camper*camper,
    log(lambda) <- al + log(hours) + b_livebait*livebait + b_persons*pers_norm,
    ap ~ dnorm(0,10),
    al ~ dnorm(0,10),
    b_livebait ~ dnorm(0,10),
    b_persons ~ dnorm(0,10),
    b_camper ~ dnorm(0,10)),
  data=d)

precis(model)
```